The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
edits spatial scale

We altered social scale based on visual (short distance) and auditory (long
distnace) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified the
distance threshold required for group assignment (see above) and re-assigned
groups at incremental distance between 5-500m. For example, at the finest social
scale, only individuals within 5m of one another were considered in the same
group, whereas at the coarset social scale, only individuals within 500m of one
another were considered in the same group.

@@

To assess the influence of spatial scale on multilayer networks, we re-sampled
our landcover classification map at varying scales. Specifically, we selected
scales relevant to caribou ecology. We re-sampled landcover using the
`grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m,
1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for
caribou during foraging <!--(REF)-->, while re-sampling at 1000m and 2500m represents
the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau
et al. 2017). Resampling occurred based on a modal moving window method, where
**XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**

For each landcover (the original resolution and modal resampled resolutions),
seasonal network layers are combined in a multilayer network <!-- Each modal
landcover, and the original are sampled and separate network layers constructed
for each. **[QW: NOT SURE WHAT THIS MEANS]** -->

>>>>

We altered social scale based on visual (short distance) and auditory (long
distnace) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified
the spatial distance threshold required for group assignment (see above) and
re-assigned groups at incremental distance between 5-500m. For example, at the
finest social scale, only individuals within 5m of one another were considered
in the same group, whereas at the coarsest social scale, individuals within 500m
of one another were considered in the same group.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover classification map at varying scales relevant to caribou ecology. We aggregated the 10m landcover raster using the R package
`grainchanger` [@Graham_2019] at five scales: 100m, 250m, 500m, and 
1000m. Aggregation occurred using a modal moving window method using a circular window corresponding to the above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making for caribou during foraging <!--(REF)-->, while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017).
